### 2009-12-18 trunk/Papers/reasoning-challenges/conclusion.tex
Some more details on infrastructure, some references (not cited yet)
new levels

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

This new approach has advantages for each of the three groups of people involved in a competition, the organisers, the participants, and the audience (which usually includes organisers and participants).

\begin{itemize}
  \item Organisers benefit from a mostly automated platform that is maintained by the community, which should greatly reduce the effort needed to run a competition.
  \item Participants benefit from a well-defined environment for running their systems, short feedback times after submitting a system, and a standardised test and benchmark platform for experimenting with novel algorithms.
  \item The audience, i.e., the scientific community, benefits from the improved discussion and report facilities. The scientific value of competitions is to find out \emph{why} a system shows a certain performance, not only \emph{that} it does.
\end{itemize}

\subsubsection*{Acknowledgements}
The original idea to organize a ``rolling'' competition in the CP community is due to Christian Schulte and Peter Stuckey.
